%-----------PROJECTS-----------%
\section{Project}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Pentagon Federal Credit Union
(PenFed)} $|$ \emph{SFDC Full Stack Developer}}    {}
    \resumeItemListStart
        \resumeItem {Proficiently worked on configuration and customization, Lightning Web Components on salesforce financial services cloud.}
        \resumeItem{Designed and developed apex classes, schedulable and batch apex, and their test classes for various functional needs in the project providing their test classes above 90\% coverage}
        \resumeItem{Came up with the complete technical design for the requirement and created the design document.}
        \resumeItem{Created multiple Experience Cloud pages for LWC with seamless navigation using custom metadata and Flow-Navigation Events.}
        \resumeItem{Worked on Record Triggered, Autolaunched, and Screen Flows.}
        \resumeItem{Created and implemented a completely new framework for sending new emails which would work on multiple objects since the limitation of email templates is that they can be processed on only one object}
        \resumeItem{Formulated multiple reports for client requirements and analysis purposes.}
        \resumeItem{Implemented Omni-Channel setup for case management and created reports based on case status life process.}
        \resumeItem{Involved in Deployments, technical assistance, and end-user troubleshooting for bug ﬁxes, and enhancements.}
        \resumeItem{Created Custom objects and fields and relationships between them, Converting Master Detail to lookup protected with field and object-level security.}
        \resumeItem{Trained three administrative assistants during a crucial project expansion to guarantee meticulous attention to detail.}
    \resumeItemListEnd

\resumeSubHeadingListEnd